### 2012-03-24 doc/theses/mikula/conclusion.tex
Master thesis: In progress.

We also implemented several ideas from the overview to infer XSD built-in types of elements and attributes. And we slightly extended the one existing method dealing with the inference of keys. \todo{Ako dopadli testy.}

@@

@@

>>>>

We also implemented several ideas from the overview to infer XSD built-in types of elements and attributes. And we slightly extended the one existing method dealing with the inference of keys. We experimentally demonstrated that on some input files, results of the extended method are better than results of the original method. However, we did not succeed in a search of an ideal, large enough set of test data. The testing was performed on a small set of input queries and further testing and algorithm tuning is required.

@@

\todo[inline]{Nejake prehladne zhrnutie plusov a minusov?}

@@

Besides the mentioned, our opinion is that the most urgent future work is obtaining a large enough test data set, performing proper experiments, and refining the algorithm by modification of its settings (statements inferred from join pattern occurrences, weights, etc.) according to experimental results. This process was slightly suggested in Chapter \ref{CHAPTER_experiments}.

### 2012-03-24 doc/theses/mikula/introduction.tex
Master thesis: In progress.

\section{Structure of the Work}
\todo[inline]{TODO}

>>>>

\section{Structure of the Thesis}
The thesis is structured as follows.

In Chapter 2, we introduce XML technologies used in this thesis and we briefly explain their basic principles.

Chapter 3 contains summaries of several existing approaches of XML schema inference. One of them proposes an utilisation of XQuery queries, which interests us the most.

We made an analysis of XQuery technology from a view of XML schema inference, where we suggest several ideas on how XQuery queries can be exploited in the inference process. This is a content of Chapter 4.

In Chapter 5, we discusses some essential questions that we needed to decide before a development of an algorithm.

The algorithm itself is proposed in Chapter 6. And Chapter 7 describes how to combine results of the algorithm with existing grammar inferring methods of XML schema inference.

An implementation of the proposed algorithm using a jInfer framework is described in Chapter 8. Chapter 9 then discusses performed experiments and their outcomes.
